Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-21 Moltres.tex
adds zanetti
Fixed "et al.": now it is the same everywhere
For multiple authors right way to cite is: **et al.**
http://davidson.libguides.com/c.php?g=349327&p=2357431

In a similar vein, Kophazi et. al. used iterative coupling between in-house
three-dimensional neutronic and one-dimensional heat conduction models DALTON
and THERM to analyze normal \gls{MSRE} operation as well as
channel-blocking-incident transients \cite{kophazi_development_2009}. The
Kophazi model added entrance effects of heat transfer coefficients as well as
thermal coupling between fuel channels through moderator heat conduction. More
recently, Cammi et. al. performed a 2D-axisymmetric single-channel analysis of
the \gls{MSBR} using the commercial finite element package COMSOL Multiphysics
\cite{cammi_multi-physics_2011}. That work directly solved the fuel salt
velocity field, used heterogeneous group constants in fuel and moderator
regions, and employed the \gls{COMSOL} software package intrinsically designed
for coupled multi-physics simulation.  Fiorina, Lathouwers, and their
colleagues conducted a benchmarking exercise \cite{fiorina_modelling_2013} in
which this Politecnico di Milano approach was expanded to a multi-channel model 
of the \gls{MSFR} and compared to code from the University of Delft
\cite{de_zwaan_static_2007,van_der_linden_2012} based on the approach in
\cite{kophazi_development_2009}. These models showed good agreement for
multiple accident transients.

More recently, Aufiero et.  al \cite{aufiero_development_2014} have begun to
approach transient simulations in the \gls{MSFR} within the finite volume
OpenFOAM multiphysics toolkit\cite{weller_tensorial_1998}.  This approach
benefits from pre-implemented turbulence models available in the OpenFOAM
library and captures the full-core three-dimensional geometry of the reactor
primary circuit.  OpenFOAM \gls{CFD} has additionally been shown by Laureau et
al. \cite{laureau_transient_2017} to couple well with Transient Fission Matrix
neutronics within the \gls{MSFR}.

>>>>

In a similar vein, Kophazi et al. used iterative coupling between in-house
three-dimensional neutronic and one-dimensional heat conduction models DALTON
and THERM to analyze normal \gls{MSRE} operation as well as
channel-blocking-incident transients \cite{kophazi_development_2009}. The
Kophazi model added entrance effects of heat transfer coefficients as well as
thermal coupling between fuel channels through moderator heat conduction. More
recently, Cammi et al. performed a 2D-axisymmetric single-channel analysis of
the \gls{MSBR} using the commercial finite element package COMSOL Multiphysics
\cite{cammi_multi-physics_2011}. That work directly solved the fuel salt
velocity field, used heterogeneous group constants in fuel and moderator
regions, and employed the \gls{COMSOL} software package intrinsically designed
for coupled multi-physics simulation.  Fiorina, Lathouwers, and their
colleagues conducted a benchmarking exercise \cite{fiorina_modelling_2013} in
which this Politecnico di Milano approach was expanded to a multi-channel model 
of the \gls{MSFR} and compared to code from the University of Delft
\cite{de_zwaan_static_2007,van_der_linden_2012} based on the approach in
\cite{kophazi_development_2009}. These models showed good agreement for
multiple accident transients. Meanwhile, leveraging lessons learned from these 
efforts has resulted in a multiscale approach from Zanetti et al. 
\cite{zanetti_geometric_2015} successfully combines high and low geometric 
fidelity for graphite-moderated \glspl{MSR}.

More recently, Aufiero et al. \cite{aufiero_development_2014} have begun to
approach transient simulations in the \gls{MSFR} within the finite volume
OpenFOAM multiphysics toolkit\cite{weller_tensorial_1998}.  This approach
benefits from pre-implemented turbulence models available in the OpenFOAM
library and captures the full-core three-dimensional geometry of the reactor
primary circuit.  OpenFOAM \gls{CFD} has additionally been shown by Laureau et
al. \cite{laureau_transient_2017} to couple well with Transient Fission Matrix
neutronics within the \gls{MSFR}.
